---
title: "Farm Vision Apples Mapping Views"
author: "Erich Seamon"
date: "1/20/2021"
output: pdf_document
---

## R Markdown

Farm Vision apples mapping analysis.

### Mapping View 1:  

Apple rows, coded by cultivar.  GREEN represents gala apples, BLUE represents honeycrisp.  Red observations indicate those locations where apples were hand sampled.  This view combines scans that are from the west and east sides.

```{r, echo=FALSE, message=FALSE, warning=FALSE}

library(plyr)
library(sp)
library(uncertainty)

#set local workspace

#load list of gala files
setwd("/mnt/lfs2/erichs/git/farm_vision_apples/data")
temp = list.files(pattern="b-gala")

#separate even and odd files
even_gala <- temp[c(1,3,5,7,9)]
odd_gala <- temp[c(2,4,6,8,10)]

#load list of honeycrisp files
temp = list.files(pattern="b-honeycrisp")

#separate even and odd files
odd_honeycrisp <- temp[c(1,3,5,7)]
even_honeycrisp <- temp[c(2,4,6,8)]


#BEGIN Spatial mapping loops

x=0
for (i in even_gala) {
  x <- x +1
  ii <- gsub('.{11}$', '', i)
  row <- read.csv(i, header=TRUE, strip.white = TRUE)
  row_ontree <- row[row$height.off.ground > 0,]
  row_ontree_true <- subset(row_ontree, in.calibration.sample == "True")
  odd_row_sp <- SpatialPointsDataFrame(cbind.data.frame(row_ontree$lat, row_ontree$lon),  row_ontree)
  odd_row_sp_true <- SpatialPointsDataFrame(cbind.data.frame(row_ontree_true$lat, row_ontree_true$lon),  row_ontree_true)
  if (x == 1) {
    plot(odd_row_sp, pch=19, cex=.2, col="green")
    plot(odd_row_sp_true, add = TRUE,  pch=19, cex=.2, col="red")
  } else {
  plot(odd_row_sp, add = TRUE, pch=19, cex=.2, col="green")
  plot(odd_row_sp_true, add = TRUE,  pch=19, cex=.2, col="red")
  }
}


for (i in even_honeycrisp) {
  ii <- gsub('.{11}$', '', i)
  row <- read.csv(i, header=TRUE, strip.white = TRUE)
  row_ontree <- row[row$height.off.ground > 0,]
  row_ontree_true <- subset(row_ontree, in.calibration.sample == "True")
  odd_row_sp <- SpatialPointsDataFrame(cbind.data.frame(row_ontree$lat, row_ontree$lon),  row_ontree)
  odd_row_sp_true <- SpatialPointsDataFrame(cbind.data.frame(row_ontree_true$lat, row_ontree_true$lon),  row_ontree_true)
  plot(odd_row_sp, add = TRUE, pch=19, cex=.2, col="blue")
  plot(odd_row_sp_true, add = TRUE,  pch=19, cex=.2, col="red")
}

x=0
for (i in odd_gala) {
  ii <- gsub('.{11}$', '', i)
  row <- read.csv(i, header=TRUE, strip.white = TRUE)
  row_ontree <- row[row$height.off.ground > 0,]
  row_ontree_true <- subset(row_ontree, in.calibration.sample == "True")
  odd_row_sp <- SpatialPointsDataFrame(cbind.data.frame(row_ontree$lat, row_ontree$lon),  row_ontree)
  #odd_row_sp_true <- SpatialPointsDataFrame(cbind.data.frame(row_ontree_true$lat, row_ontree_true$lon),  row_ontree_true)
  plot(odd_row_sp, add = TRUE, pch=19, cex=.2, col="green")
  #plot(odd_row_sp_true, add = TRUE,  pch=19, cex=.2, col="red")
}

for (i in odd_honeycrisp) {
  ii <- gsub('.{11}$', '', i)
  row <- read.csv(i, header=TRUE, strip.white = TRUE)
  row_ontree <- row[row$height.off.ground > 0,]
  row_ontree_true <- subset(row_ontree, in.calibration.sample == "True")
  odd_row_sp <- SpatialPointsDataFrame(cbind.data.frame(row_ontree$lat, row_ontree$lon),  row_ontree)
  #odd_row_sp_true <- SpatialPointsDataFrame(cbind.data.frame(row_ontree_true$lat, row_ontree_true$lon),  row_ontree_true)
  plot(odd_row_sp, add = TRUE, pch=19, cex=.2, col="blue")
  #plot(odd_row_sp_true, add = TRUE,  pch=19, cex=.2, col="red")
}

#END - Spatial Mapping loops




```


### Mapping View 2:  

Apple rows, coded by east and west scans.   Red observations indicate those locations where apples were hand sampled. 


```{r, echo=FALSE, message=FALSE, warning=FALSE}


library(plyr)
library(sp)
library(uncertainty)

#set local workspace

#load list of gala files
setwd("/mnt/lfs2/erichs/git/farm_vision_apples/data")
temp = list.files(pattern="b-gala")

#separate even and odd files
even_gala <- temp[c(1,3,5,7,9)]
odd_gala <- temp[c(2,4,6,8,10)]

#load list of honeycrisp files
temp = list.files(pattern="b-honeycrisp")

#separate even and odd files
odd_honeycrisp <- temp[c(1,3,5,7)]
even_honeycrisp <- temp[c(2,4,6,8)]
#BEGIN Spatial mapping loops EW

x=0
for (i in even_gala) {
    x <- x +1
  ii <- gsub('.{11}$', '', i)
  row <- read.csv(i, header=TRUE, strip.white = TRUE)
  row_ontree <- row[row$height.off.ground > 0,]
  row_ontree_true <- subset(row_ontree, in.calibration.sample == "True")
  
  row_ontree_E <- row_ontree[row_ontree$side == "E",]
  row_ontree_W <- row_ontree[row_ontree$side == "W",]
  
  odd_row_sp <- SpatialPointsDataFrame(cbind.data.frame(row_ontree$lat, row_ontree$lon),  row_ontree)
  odd_row_sp_true <- SpatialPointsDataFrame(cbind.data.frame(row_ontree_true$lat, row_ontree_true$lon),  row_ontree_true)
  odd_row_sp_E <- SpatialPointsDataFrame(cbind.data.frame(row_ontree_E$lat, row_ontree_E$lon),  row_ontree_E)
  odd_row_sp_W <- SpatialPointsDataFrame(cbind.data.frame(row_ontree_W$lat, row_ontree_W$lon),  row_ontree_W)
   if (x == 1) {
    plot(odd_row_sp_W, pch=19, cex=.2, col="green")
    plot(odd_row_sp_E, add = TRUE, pch=19, cex=.2, col="blue")
    plot(odd_row_sp_true, add = TRUE,  pch=19, cex=.2, col="red")
  } else {
  plot(odd_row_sp_W, add = TRUE, pch=19, cex=.2, col="green")
  plot(odd_row_sp_E, add = TRUE, pch=19, cex=.2, col="blue")
  plot(odd_row_sp_true, add = TRUE,  pch=19, cex=.2, col="red")
  }
}

for (i in even_honeycrisp) {
  ii <- gsub('.{11}$', '', i)
  row <- read.csv(i, header=TRUE, strip.white = TRUE)
  row_ontree <- row[row$height.off.ground > 0,]
  row_ontree_true <- subset(row_ontree, in.calibration.sample == "True")
  
  row_ontree_E <- row_ontree[row_ontree$side == "E",]
  row_ontree_W <- row_ontree[row_ontree$side == "W",]
  
  odd_row_sp <- SpatialPointsDataFrame(cbind.data.frame(row_ontree$lat, row_ontree$lon),  row_ontree)
  odd_row_sp_true <- SpatialPointsDataFrame(cbind.data.frame(row_ontree_true$lat, row_ontree_true$lon),  row_ontree_true)
  odd_row_sp_E <- SpatialPointsDataFrame(cbind.data.frame(row_ontree_E$lat, row_ontree_E$lon),  row_ontree_E)
  odd_row_sp_W <- SpatialPointsDataFrame(cbind.data.frame(row_ontree_W$lat, row_ontree_W$lon),  row_ontree_W)
  
  plot(odd_row_sp_W, add = TRUE, pch=19, cex=.2, col="green")
  plot(odd_row_sp_E, add = TRUE, pch=19, cex=.2, col="blue")
  plot(odd_row_sp_true, add = TRUE,  pch=19, cex=.2, col="red")
}

for (i in odd_gala) {
  ii <- gsub('.{11}$', '', i)
  row <- read.csv(i, header=TRUE, strip.white = TRUE)
  row_ontree <- row[row$height.off.ground > 0,]
  row_ontree_true <- subset(row_ontree, in.calibration.sample == "True")
  
  row_ontree_E <- row_ontree[row_ontree$side == "E",]
  row_ontree_W <- row_ontree[row_ontree$side == "W",]
  
  odd_row_sp <- SpatialPointsDataFrame(cbind.data.frame(row_ontree$lat, row_ontree$lon),  row_ontree)
  #odd_row_sp_true <- SpatialPointsDataFrame(cbind.data.frame(row_ontree_true$lat, row_ontree_true$lon),  row_ontree_true)
  odd_row_sp_E <- SpatialPointsDataFrame(cbind.data.frame(row_ontree_E$lat, row_ontree_E$lon),  row_ontree_E)
  odd_row_sp_W <- SpatialPointsDataFrame(cbind.data.frame(row_ontree_W$lat, row_ontree_W$lon),  row_ontree_W)
  
  plot(odd_row_sp_W, add = TRUE, pch=19, cex=.2, col="green")
  plot(odd_row_sp_E, add = TRUE, pch=19, cex=.2, col="blue")
  #plot(odd_row_sp_true, add = TRUE,  pch=19, cex=.2, col="red")
}

for (i in odd_honeycrisp) {
  ii <- gsub('.{11}$', '', i)
  row <- read.csv(i, header=TRUE, strip.white = TRUE)
  row_ontree <- row[row$height.off.ground > 0,]
  row_ontree_true <- subset(row_ontree, in.calibration.sample == "True")
  
  row_ontree_E <- row_ontree[row_ontree$side == "E",]
  row_ontree_W <- row_ontree[row_ontree$side == "W",]
  
  odd_row_sp <- SpatialPointsDataFrame(cbind.data.frame(row_ontree$lat, row_ontree$lon),  row_ontree)
  #odd_row_sp_true <- SpatialPointsDataFrame(cbind.data.frame(row_ontree_true$lat, row_ontree_true$lon),  row_ontree_true)
  odd_row_sp_E <- SpatialPointsDataFrame(cbind.data.frame(row_ontree_E$lat, row_ontree_E$lon),  row_ontree_E)
  odd_row_sp_W <- SpatialPointsDataFrame(cbind.data.frame(row_ontree_W$lat, row_ontree_W$lon),  row_ontree_W)
  
  plot(odd_row_sp_W, add = TRUE, pch=19, cex=.2, col="green")
  plot(odd_row_sp_E, add = TRUE, pch=19, cex=.2, col="blue")
  #plot(odd_row_sp_true, add = TRUE,  pch=19, cex=.2, col="red")
}

```
