---
title: "Farm Vision Apples Analysis"
author: "Erich Seamon"
date: "1/22/2021"
output: pdf_document
---

## Summary

The following code loads all data (calibration and actual scan data), bootstraps the calibration data's H/W and HW ratios, then uses the sample mean distributions per row to estimate HW ratios for all scan observations (even rows use nearest odd row's calibration sample distribution).  Using this sampled HW ratio, we then calculate a volume of an oblate ellipsoid, using the radius the major axis (width), an estimating height.  We then use literature an estimated density calculation (0.8 g/cm3) to estimate yields per row, per cultivar, and total overall.

```{r, warning=FALSE, echo=FALSE}
library(plyr)
library(sp)
library(uncertainty)
library(pdqr)
library(magrittr)

options(scipen=999)
options(warn=-1)


#set local workspace
setwd("/mnt/lfs2/erichs/git/farm_vision_apples/data")

#load list of gala files
temp = list.files(pattern="b-gala")

#separate even and odd files
even_gala <- temp[c(1,3,5,7,9)]
odd_gala <- temp[c(2,4,6,8,10)]

#load list of honeycrisp files
temp = list.files(pattern="b-honeycrisp")

#separate even and odd files
odd_honeycrisp <- temp[c(1,3,5,7)]
even_honeycrisp <- temp[c(2,4,6,8)]

#load calibration dataset
calibration <- read.csv("hand-counts-and-sizes.csv", header=TRUE)

#oblate ellipsoid calibration calculation
calibration$west_A_volume <- (4/3 *pi * calibration$west_width_A^2 * calibration$west_height_A)
calibration$west_B_volume <- (4/3 *pi * calibration$west_width_B^2 * calibration$west_height_B)
calibration$west_C_volume <- (4/3 *pi * calibration$east_width_C^2 * calibration$east_height_C)
calibration$west_D_volume <- (4/3 *pi * calibration$east_width_D^2 * calibration$east_height_D)

#initial calibration volume uncertainty 

#calculate calibration uncertainty for volume
calibration$uncertainty <- sqrt(rowSums((calibration[12:15] - rowMeans(calibration[12:15]))^2)/4)

#calculate calibration uncertainy +/- percentage
calibration$uncertainty_pct <- calibration$uncertainty / rowMeans(calibration[12:15]) 



#Calculate Ratios for Height/Width

#calculate calibration H/W ratio
calibration$ratio_west_A <- calibration$west_height_A/calibration$west_width_A
calibration$ratio_west_B <- calibration$west_height_B/calibration$west_width_B
calibration$ratio_east_C <- calibration$east_height_C/calibration$east_width_C
calibration$ratio_east_D <- calibration$east_height_D/calibration$east_width_D


#initial calibration ratio uncertainty

#calculate calibration uncertainty for ratio
calibration$uncertainty <- sqrt(rowSums((calibration[12:15] - rowMeans(calibration[12:15]))^2)/4)

#calculate calibration uncertainy +/- percentage
calibration$uncertainty_pct <- calibration$uncertainty / rowMeans(calibration[12:15]) 


#----------------


#BEGIN Even row calibration MERGE


even_gala_calibration <- NULL
even_gala_final <- NULL
for (i in even_gala) {
  ii <- gsub('.{11}$', '', i)
    row <- read.csv(i, header=TRUE, strip.white = TRUE)
    row$radius.in.mm <- row$radius.in.mm * 1000
    row_ontree <- row[row$height.off.ground > 0,]
    row_ontree_true <- subset(row_ontree, in.calibration.sample == "True")
    
    set.seed(101)
    cal <- calibration[calibration$name == ii,]
    # Using ordinary bootstrap
    r_dis_mean <- as.numeric(cal[,c(18,19,20,21)]) %>% 
      new_r(type = "continuous") %>% 
      form_estimate(stat = mean, sample_size = cal[,3])
    
    ci <- summ_quantile(r_dis_mean,probs = c(.05,.95))
    
    row_ontree$ratio_est_top <- ci[1]
    row_ontree$ratio_est_bottom <- ci[2]
    row_ontree$ratio_est <- r_dis_mean(nrow(row_ontree))
    row_ontree$height_est <- (row_ontree$radius.in.mm * row_ontree$ratio_est)
    row_ontree$height_est_top <- (row_ontree$radius.in.mm * row_ontree$ratio_est_top)
    row_ontree$height_est_bottom <- (row_ontree$radius.in.mm * row_ontree$ratio_est_bottom)
    
    row_ontree$volume <- ((4/3) * pi * row_ontree$radius.in.mm * row_ontree$radius.in.mm * row_ontree$height_est)
    row_ontree$volume_top <- ((4/3) * pi * row_ontree$radius.in.mm * row_ontree$radius.in.mm * row_ontree$height_est_top)
    row_ontree$volume_bottom <- ((4/3) * pi * row_ontree$radius.in.mm * row_ontree$radius.in.mm * row_ontree$height_est_bottom)
    row_ontree$name <- ii
    even_gala_final <- rbind(even_gala_final, row_ontree)
    
    odd_row_sp <- SpatialPointsDataFrame(cbind.data.frame(row_ontree$lat, row_ontree$lon),  row_ontree)
    odd_row_sp_true <- SpatialPointsDataFrame(cbind.data.frame(row_ontree_true$lat, row_ontree_true$lon),  row_ontree_true)
    row_ontree_true_E <- row_ontree_true[row_ontree_true$side == "E",]
    row_ontree_true_W <- row_ontree_true[row_ontree_true$side == "W",]
    
    calibration_row <- calibration[calibration$name == ii,]
    df.expanded_E <- calibration_row[rep(row.names(calibration_row), nrow(row_ontree_true_E)), ]
    df.expanded_W <- calibration_row[rep(row.names(calibration_row), nrow(row_ontree_true_W)), ]
    
    row_calibration_combined_E <- cbind(row_ontree_true_E, df.expanded_E)
    row_calibration_combined_W <- cbind(row_ontree_true_W, df.expanded_W)
    
    row_calibration_combined_W$height <- (row_calibration_combined_W$radius.in.mm * rowMeans(row_calibration_combined_W[27:28]))
    row_calibration_combined_E$height <- (row_calibration_combined_E$radius.in.mm * rowMeans(row_calibration_combined_E[29:30]))
    
    row_calibration_combined_E$volume <- ((4/3) * pi * row_calibration_combined_E$radius.in.mm * row_calibration_combined_E$radius.in.mm * row_calibration_combined_E$height)
    row_calibration_combined_W$volume <- ((4/3) * pi * row_calibration_combined_W$radius.in.mm * row_calibration_combined_W$radius.in.mm * row_calibration_combined_W$height)
    gala_cal <- rbind(row_calibration_combined_E,row_calibration_combined_W)
    even_gala_calibration <- rbind(even_gala_calibration, gala_cal)
    
  
}





even_honeycrisp_calibration <- NULL
even_honeycrisp_final <- NULL
for (i in even_honeycrisp) {
  ii <- gsub('.{11}$', '', i)
  row <- read.csv(i, header=TRUE, strip.white = TRUE)
  row$radius.in.mm <- row$radius.in.mm * 1000
  row_ontree <- row[row$height.off.ground > 0,]
  row_ontree_true <- subset(row_ontree, in.calibration.sample == "True")
  
  set.seed(101)
  cal <- calibration[calibration$name == ii,]
  # Using ordinary bootstrap
  r_dis_mean <- as.numeric(cal[,c(18,19,20,21)]) %>% 
    new_r(type = "continuous") %>% 
    form_estimate(stat = mean, sample_size = cal[,3])
  
  ci <- summ_quantile(r_dis_mean,probs = c(.05,.95))
  
  row_ontree$ratio_est_top <- ci[1]
  row_ontree$ratio_est_bottom <- ci[2]
  row_ontree$ratio_est <- r_dis_mean(nrow(row_ontree))
  row_ontree$height_est <- (row_ontree$radius.in.mm * row_ontree$ratio_est)
  row_ontree$height_est_top <- (row_ontree$radius.in.mm * row_ontree$ratio_est_top)
  row_ontree$height_est_bottom <- (row_ontree$radius.in.mm * row_ontree$ratio_est_bottom)
  
  row_ontree$volume <- ((4/3) * pi * row_ontree$radius.in.mm * row_ontree$radius.in.mm * row_ontree$height_est)
  row_ontree$volume_top <- ((4/3) * pi * row_ontree$radius.in.mm * row_ontree$radius.in.mm * row_ontree$height_est_top)
  row_ontree$volume_bottom <- ((4/3) * pi * row_ontree$radius.in.mm * row_ontree$radius.in.mm * row_ontree$height_est_bottom)
  row_ontree$name <- ii
  even_honeycrisp_final <- rbind(even_honeycrisp_final, row_ontree)
  
  #odd_row_sp <- SpatialPointsDataFrame(cbind.data.frame(row_ontree$lat, row_ontree$lon),  row_ontree)
  #odd_row_sp_true <- SpatialPointsDataFrame(cbind.data.frame(row_ontree_true$lat, row_ontree_true$lon),  row_ontree_true)
  row_ontree_true_E <- row_ontree_true[row_ontree_true$side == "E",]
  row_ontree_true_W <- row_ontree_true[row_ontree_true$side == "W",]
  
  calibration_row <- calibration[calibration$name == ii,]
  df.expanded_E <- calibration_row[rep(row.names(calibration_row), nrow(row_ontree_true_E)), ]
  df.expanded_W <- calibration_row[rep(row.names(calibration_row), nrow(row_ontree_true_W)), ]
  
  row_calibration_combined_E <- cbind(row_ontree_true_E, df.expanded_E)
  row_calibration_combined_W <- cbind(row_ontree_true_W, df.expanded_W)
  
  row_calibration_combined_W$height <- (row_calibration_combined_W$radius.in.mm * rowMeans(row_calibration_combined_W[27:28]))
  row_calibration_combined_E$height <- (row_calibration_combined_E$radius.in.mm * rowMeans(row_calibration_combined_E[29:30]))
  
  row_calibration_combined_E$volume <- ((4/3) * pi * row_calibration_combined_E$radius.in.mm * row_calibration_combined_E$radius.in.mm * row_calibration_combined_E$height)
  row_calibration_combined_W$volume <- ((4/3) * pi * row_calibration_combined_W$radius.in.mm * row_calibration_combined_W$radius.in.mm * row_calibration_combined_W$height)
  honeycrisp_cal <- rbind(row_calibration_combined_E,row_calibration_combined_W)
  even_honeycrisp_calibration <- rbind(even_honeycrisp_calibration, honeycrisp_cal)
  
  
}



#BEGIN odd row 


odd_gala_final <- NULL
for (i in odd_gala) {
  ii <- gsub('.{11}$', '', i)
  row <- read.csv(i, header=TRUE, strip.white = TRUE)
  row$radius.in.mm <- row$radius.in.mm * 1000
  row_ontree <- row[row$height.off.ground > 0,]
  row_ontree_true <- subset(row_ontree, in.calibration.sample == "True")
  
  
  iii <- as.numeric(strsplit(ii, "\\D+")[[1]][-1])
  iii <- iii+1
  iii <- paste(gsub("\\d+", "", ii), iii, sep="")
  
  
  set.seed(101)
  cal <- calibration[calibration$name == iii,]
  # Using ordinary bootstrap
  r_dis_mean <- as.numeric(cal[,c(18,19,20,21)]) %>% 
    new_r(type = "continuous") %>% 
    form_estimate(stat = mean, sample_size = cal[,3])
  
  
  ci <- summ_quantile(r_dis_mean,probs = c(.05,.95))
  
  row_ontree$ratio_est_top <- ci[1]
  row_ontree$ratio_est_bottom <- ci[2]
  row_ontree$ratio_est <- r_dis_mean(nrow(row_ontree))
  row_ontree$height_est <- (row_ontree$radius.in.mm * row_ontree$ratio_est)
  row_ontree$height_est_top <- (row_ontree$radius.in.mm * row_ontree$ratio_est_top)
  row_ontree$height_est_bottom <- (row_ontree$radius.in.mm * row_ontree$ratio_est_bottom)
  
  row_ontree$volume <- ((4/3) * pi * row_ontree$radius.in.mm * row_ontree$radius.in.mm * row_ontree$height_est)
  row_ontree$volume_top <- ((4/3) * pi * row_ontree$radius.in.mm * row_ontree$radius.in.mm * row_ontree$height_est_top)
  row_ontree$volume_bottom <- ((4/3) * pi * row_ontree$radius.in.mm * row_ontree$radius.in.mm * row_ontree$height_est_bottom)
  row_ontree$name <- ii
  odd_gala_final <- rbind(odd_gala_final, row_ontree)
  

}



odd_honeycrisp_final<- NULL
for (i in odd_honeycrisp) {
  ii <- gsub('.{11}$', '', i)
  row <- read.csv(i, header=TRUE, strip.white = TRUE)
  row$radius.in.mm <- row$radius.in.mm * 1000
  row_ontree <- row[row$height.off.ground > 0,]
  row_ontree_true <- subset(row_ontree, in.calibration.sample == "True")
  
  
  iii <- as.numeric(strsplit(ii, "\\D+")[[1]][-1])
  iii <- iii+1
  iii <- paste(gsub("\\d+", "", ii), iii, sep="")
  
  
  set.seed(101)
  cal <- calibration[calibration$name == iii,]
  # Using ordinary bootstrap
  r_dis_mean <- as.numeric(cal[,c(18,19,20,21)]) %>% 
    new_r(type = "continuous") %>% 
    form_estimate(stat = mean, sample_size = cal[,3])
  
  
  ci <- summ_quantile(r_dis_mean,probs = c(.05,.95))
  
  row_ontree$ratio_est_top <- ci[1]
  row_ontree$ratio_est_bottom <- ci[2]
  row_ontree$ratio_est <- r_dis_mean(nrow(row_ontree))
  row_ontree$height_est <- (row_ontree$radius.in.mm * row_ontree$ratio_est)
  row_ontree$height_est_top <- (row_ontree$radius.in.mm * row_ontree$ratio_est_top)
  row_ontree$height_est_bottom <- (row_ontree$radius.in.mm * row_ontree$ratio_est_bottom)
  
  row_ontree$volume <- ((4/3) * pi * row_ontree$radius.in.mm * row_ontree$radius.in.mm * row_ontree$height_est)
  row_ontree$volume_top <- ((4/3) * pi * row_ontree$radius.in.mm * row_ontree$radius.in.mm * row_ontree$height_est_top)
  row_ontree$volume_bottom <- ((4/3) * pi * row_ontree$radius.in.mm * row_ontree$radius.in.mm * row_ontree$height_est_bottom)
  row_ontree$name <- ii
  odd_honeycrisp_final <- rbind(odd_honeycrisp_final, row_ontree)
  
  
}



#Weight calc

odd_honeycrisp_final$weight <- (odd_honeycrisp_final$volume/1000) * .8
odd_gala_final$weight <- (odd_gala_final$volume/1000) * .8
even_honeycrisp_final$weight <- (even_honeycrisp_final$volume/1000) * .8
even_gala_final$weight <- (even_gala_final$volume/1000) * .8


odd_honeycrisp_final$weight_top <- (odd_honeycrisp_final$volume_top/1000) * .8
odd_gala_final$weight_top <- (odd_gala_final$volume_top/1000) * .8
even_honeycrisp_final$weight_top <- (even_honeycrisp_final$volume_top/1000) * .8
even_gala_final$weight_top <- (even_gala_final$volume_top/1000) * .8


odd_honeycrisp_final$weight_bottom <- (odd_honeycrisp_final$volume_bottom/1000) * .8
odd_gala_final$weight_bottom <- (odd_gala_final$volume_bottom/1000) * .8
even_honeycrisp_final$weight_bottom <- (even_honeycrisp_final$volume_bottom/1000) * .8
even_gala_final$weight_bottom <- (even_gala_final$volume_bottom/1000) * .8


finaldata <- rbind(odd_honeycrisp_final, odd_gala_final, even_honeycrisp_final, even_gala_final)

weight <- aggregate(finaldata$weight, by=list(finaldata$name), FUN = "sum")
weight_top <- aggregate(finaldata$weight_top, by=list(finaldata$name), FUN = "sum")
weight_bottom <- aggregate(finaldata$weight_bottom, by=list(finaldata$name), FUN = "sum")

finalweight <- cbind(weight, weight_top[,2], weight_bottom[,2])
colnames(finalweight) <- c("name", "weight", "weight_top", "weight_bottom")


finalweight$index <- c(1,10,11,12,17,18,2,3,4,9,13,14,15,16,5,6,7,8)
finalweight <- finalweight[order(finalweight$index), ]

finalweight$weight_kg <- finalweight$weight/1000
finalweight$weight_top_kg <- finalweight$weight_top/1000
finalweight$weight_bottom_kg <- finalweight$weight_bottom/1000

finalweight$weight_lbs <- finalweight$weight/453.59237
finalweight$weight_top_lbs <- finalweight$weight_top/453.59237
finalweight$weight_bottom_lbs <- finalweight$weight_bottom/453.59237

# 
# 
# plot(finalweight$weight)
# lines(finalweight$weight, col="black")
# points(finalweight$weight_top, col = "red")
# lines(finalweight$weight_top, col = "red")
# points(finalweight$weight_bottom, col = "red")
# lines(finalweight$weight_bottom, col = "red")




plot(finalweight$weight_lbs,  xlab = "", main="Total apples weight per row (lbs)",  ylab="LBS", axes=FALSE)
axis(side = 1, c(1:18), c(as.character(finalweight$name)), las=2)
axis(side = 2, at = c(2000,4000,6000,8000,10000,12000,14000))
box()

lines(finalweight$weight_lbs, col="black")
points(finalweight$weight_top_lbs, col = "red")
lines(finalweight$weight_top_lbs, col = "red")
points(finalweight$weight_bottom_lbs, col = "red")
lines(finalweight$weight_bottom_lbs, col = "red")





row.names(finalweight) <- finalweight$index

gala_finalweight <- finalweight[c(1,2,3,4,9,10,11,12,17,18),]


# 
# plot(gala_finalweight$weight_lbs, ylim=c(2000, 15000), main="GALA total apples weight per row (lbs)", xlab = "rows", ylab="LBS")
# lines(gala_finalweight$weight_lbs, col="black")
# points(gala_finalweight$weight_top_lbs, col = "red")
# lines(gala_finalweight$weight_top_lbs, col = "red")
# points(gala_finalweight$weight_bottom_lbs, col = "red")
# lines(gala_finalweight$weight_bottom_lbs, col = "red")


honeycrisp_finalweight <- finalweight[c(5,6,7,8,9,11,12,13,4),]


# 
# plot(honeycrisp_finalweight$weight_lbs, ylim=c(2000, 15000), main="HONEYCRISP total apples weight per row (lbs)",  xlab = "rows", ylab="LBS")
# axis(side = 1, c(1:9), c(as.character(honeycrisp_finalweight$name)), las=2)
# 
# lines(honeycrisp_finalweight$weight_lbs, col="black")
# points(honeycrisp_finalweight$weight_top_lbs, col = "red")
# lines(honeycrisp_finalweight$weight_top_lbs, col = "red")
# points(honeycrisp_finalweight$weight_bottom_lbs, col = "red")
# lines(honeycrisp_finalweight$weight_bottom_lbs, col = "red")
# 



honeycrisp_totals_lbs <- cbind(sum(honeycrisp_finalweight$weight_lbs), sum(honeycrisp_finalweight$weight_top_lbs), sum(honeycrisp_finalweight$weight_bottom_lbs))
gala_totals_lbs <- cbind(sum(gala_finalweight$weight_lbs), sum(gala_finalweight$weight_top_lbs), sum(gala_finalweight$weight_bottom_lbs))
finalweight_lbs <-  cbind(sum(finalweight$weight_lbs), sum(finalweight$weight_top_lbs), sum(finalweight$weight_bottom_lbs))






```
\newpage

```{r, warning=FALSE, echo=FALSE}

library(knitr)

kable(finalweight[, c(1,9:11)])


all_table <- data.frame(colSums(finalweight[c(9:11)]))
colnames(all_table) <- c("gala and honeycrisp")
kable(all_table)

honeycrisp_table <- data.frame(colSums(honeycrisp_finalweight[c(9:11)]))
colnames(honeycrisp_table) <- c("honeycrisp")
kable(honeycrisp_table)


gala_table <- data.frame(colSums(gala_finalweight[c(9:11)]))
colnames(gala_table) <- c("gala")
kable(gala_table)
```